Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Started working on regression models

\subsubsection{Regression Model} 
In order to examine the relative effect of each factor on participants' VURs, we constructed a statistical model to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We performed a binary logistic regression using generalized estimating equations, which accounts for our repeated measures experimental design (i.e., each participant contributed multiple data points).

>>>>

\subsubsection{Regression Model} 
In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points). Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).

\begin{table}
\centering
\begin{tabular}{|l| r|}
\hline
Variables Included & QIC\\
\hline
\hline
(Intercept) & 18,539.3\\
\hline
Device Type & 18,122.9\\
\hline
Data Recipient & 17,383.6\\
\hline
IUIPC (covariate) & 17,725.6\\
\hline
Data Type & 14,794.5\\
\hline
Device Type & \\
Data Recipient & \\
Data Type & 13,942.9\\
\hline
Data Recipient & \\
Data Type & 13,951.2\\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.}
\label{regression}
\end{table}
